Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-03-23 awipev-CO2.Rmd
sal_mix and temp_mix modifications done

# Conversion of spectro pH to a same T°
pH_seafet <- d %>%
  dplyr::filter(!is.na(pH_s_seafet))
pH_seafet <- pH_seafet %>%
  dplyr::mutate(pH_s_seafet_temp_field = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_field, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$salinity_field,Pt=0,Sit=0))

pH_durafet <- d %>%
  dplyr::filter(!is.na(pH_s_durafet))
pH_durafet <- pH_durafet %>%
  dplyr::mutate(pH_s_durafet_temp_field = pHinsi(pH=pH_durafet$pH_s_durafet,ALK=pH_durafet$at_mean_interp*1e-6, Tinsi=pH_durafet$temp_field, Tlab=pH_durafet$temp_s_lab, Pinsi= pH_durafet$depth/10, S=pH_durafet$salinity_field,Pt=0,Sit=0))

# create separate seafet/durafet df to join to initial "d" df
pH_seafet_mean <- pH_seafet%>%
  dplyr::select(datetime,pH_s_seafet_temp_field)%>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(pH_s_seafet_temp_field = mean(pH_s_seafet_temp_field, na.rm = T))
pH_durafet_mean <- pH_durafet%>%
  dplyr::select(datetime,pH_s_durafet_temp_field)%>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(pH_s_durafet_temp_field = mean(pH_s_durafet_temp_field, na.rm = T))

@@

```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour.rds"))
# load = d_hour
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT_filtered, NA), # beginning of data series for AT
         AT_filtered = ifelse(AT_filtered == "NaN", NA, AT_filtered), #3 columns are character
         #pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
         #PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
         ) %>%
  dplyr::rename(at_contros=AT,pco2_contros=PCO2_corr_contros_filtered,pH_durafet=HW_pH1_filtered,temp_insitu=Temp_SBE38_filtered, sal_fb=sal_fb_filtered, sal_insitu=sal_insitu_filtered, sal=sal_filtered, temp_fb=temp_fb_filtered)
```

@@

# seaFET pH 
# closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
# discrete$closest_datetime <- d_all$datetime[closest]
# # if the closest value is more than 30 min away, then we do not take it
# discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, pH_s_seafet_temp_field) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")
# #voltINT
# discrete2merge <- discrete %>%
#   #drop_na() %>%
#   dplyr::select(closest_datetime, voltINT) %>%
#   rename(datetime=closest_datetime)
# d_all <- full_join(d_all, discrete2merge, by="datetime")
# #voltEXT
# discrete2merge <- discrete %>%
#   #drop_na() %>%
#   dplyr::select(closest_datetime, voltEXT) %>%
#   rename(datetime=closest_datetime)
# d_all <- full_join(d_all, discrete2merge, by="datetime")

# duraFET pH 
# closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
# discrete$closest_datetime <- d_all$datetime[closest]
# # if the closest value is more than 30 min away, then we do not take it
# discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, pH_s_durafet_temp_field) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

@@

@@

#SAL
sal_xts <- dplyr::select(d_all, datetime, sal)%>%
  dplyr::filter(sal >28)

@@

      dySeries("sal", color = "blue", strokeWidth = 0, label = "S") %>%

@@

temp_insitu_xts <- dplyr::select(d_all, datetime, temp_insitu)

@@

dygraph(temp_insitu_xts, group = "awipev", main="Temperature (in situ)", ylab="Temperature") %>%
      dySeries("temp_insitu", color = "blue", strokeWidth = 0, label = "T") %>%

@@

durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_field)

@@

    dySeries("pH_s_durafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%

@@

seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_field)

@@

  dySeries("pH_s_seafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%

@@

```{r water masses, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
# One tries to identify water masses coming from the Atlantic or freshwater

@@

## Salinities
Several salinity sensors are on site, 1 inside the Ferrybox and 1 outside. Note that several CTD have been replace in situ. The sal_insitu variable combine all these CTD salinity measurements:

- 1 SBE45 inside the Ferrybox (sal_fb)
- 1 CTD at 11 meters depth (sal_insitu)

@@

### **Sal FB / Sal *in situ* **
```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE}

d_all <- d_all%>%
  dplyr::mutate( sal = ifelse(sal <28, NA, sal) ,
                 sal_fb = ifelse(sal_fb <28, NA, sal_fb),
                 sal_insitu = ifelse(sal_insitu <28, NA, sal_insitu))
  d_all <- d_all%>%
  dplyr::mutate( sal = ifelse(datetime > "2019-12-26 00:00:00", NA, sal),
                 sal_insitu = ifelse(datetime > "2019-12-26 00:00:00", NA, sal_insitu))

fit <- lmodel2(data = d_all,  sal_fb ~ sal_insitu , nperm = 99)

p_sal_fb_sal_insitu<-  ggplot(d_all,aes(x=sal_insitu, y= sal_fb, label = month))+
  geom_text( aes(color=factor(month))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_line(aes(x = sal_fb, y = sal_fb), linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("Sal in situ vs Sal FB","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
  labs( x="Salinity insitu", y="Salinity FB ", color = "Months")  +theme_bw()
print(p_sal_fb_sal_insitu)

The mean difference between salinity FB and in situ is: `r mean_diff_sal_fb_insitu` ± `r sd_diff_sal_fb_insitu`°C.

## Temperatures
Several temperature sensors are on site, 1 inside the Ferrybox and 2 outside:

- 1 SBE45 inside the Ferrybox (temp_fb)
- 1 seaFET T°C inside the seaFET at 11 meters depth (T_seaF)
- 1 SBE38 at 11 meters depth (temp_insitu)

### **T seaFET / T in situ **
```{r Temp comparaison, echo=FALSE, message= FALSE, warning=FALSE}
# seaF outliers (T - volt int - volt ext) to remove from 2017-12-10 to 2017-12-14
d_all <- d_all %>%
  dplyr::mutate(T_seaF = ifelse(datetime >= "2017-12-10 11:00:00" & datetime <= "2017-12-14 12:00:00", NA, T_seaF),
                voltINT = ifelse(datetime >= "2017-12-10 11:00:00" & datetime <= "2017-12-14 12:00:00", NA, voltINT), 
                voltEXT = ifelse(datetime >= "2017-12-10 11:00:00" & datetime <= "2017-12-14 12:00:00", NA, voltEXT))

fit <- lmodel2(data = d_all,  T_seaF ~ temp_insitu , nperm = 99)

pTseaf_Tinsi<-  ggplot(d_all,aes(x=temp_insitu, y= T_seaF, label = month))+
  geom_text( aes(color=factor(month))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_line(aes(x = T_seaF, y = T_seaF), linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("T seaF vs T insi","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
  labs( x="T insi", y="T seaF ", color = "Months")  +theme_bw()
print(pTseaf_Tinsi)

d_all$diff_T_seaF_insitu <- d_all$T_seaF - d_all$temp_insitu
mean_diff_T_seaF_insitu <- round(mean(d_all$diff_T_seaF_insitu, na.rm = TRUE), digits = 2)
sd_diff_T_seaF_insitu <- round(sd(d_all$diff_T_seaF_insitu, na.rm = TRUE), digits = 2)

@@

### **T Ferrybox / T in situ **
```{r Temp fb insi comparaison, echo=FALSE, message= FALSE, warning=FALSE}
# Remove temp_fb outliers 
d_all <- d_all %>%
  dplyr::mutate(temp_fb = ifelse(datetime >= "2017-03-22 08:00:00" & datetime <= "2017-03-23 16:00:00", NA, temp_fb),
                temp_fb = ifelse(temp_fb >15, NA, temp_fb))

fit <- lmodel2(data = d_all,  temp_fb ~ temp_insitu , nperm = 99)

pTfb_Tinsi<-  ggplot(d_all,aes(x=temp_insitu, y= temp_fb, label = month))+
  geom_text( aes(color=factor(month))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_line(aes(x = temp_fb, y = temp_fb), linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("T FB vs T insi","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
  labs( x="T insi", y="T FB ", color = "Months")  +theme_bw()
print(pTfb_Tinsi)

d_all$diff_T_fb_insitu <- d_all$T_seaF - d_all$temp_insitu
mean_diff_T_fb_insitu <- round(mean(d_all$diff_T_fb_insitu, na.rm = TRUE), digits = 2)
sd_diff_T_fb_insitu <- round(sd(d_all$diff_T_fb_insitu, na.rm = TRUE), digits = 2)
```

@@

@@

```{r TA 2nd cleaning , echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}

@@

```{r Discrete salinity vs TA, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%", fig.align="center"}
d_all_at_discrete <- d_all %>% #  To remove an outlier in red
  dplyr::select(datetime, month,closest_datetime, at, sal)%>%
  dplyr::filter( !is.na(at) & !is.na(sal) & sal >30)

@@

#fit <- lm(data = drop_na(d_all_at_discrete, at), at ~ sal)
fit <- lm(data = d_all_at_discrete, at ~ sal)
slope_s_at <- fit$coefficients[[2]]
intercept_s_at <- fit$coefficients[[1]]
# at_s <- ggreg(fit)+ labs(x="Salinity", y="Discrete TA") + Mytheme()

>>>>

# Conversion of spectro pH to a same T°
pH_seafet <- d %>%
  dplyr::filter(!is.na(pH_s_seafet))
pH_seafet <- pH_seafet %>%
  dplyr::mutate(pH_s_seafet_temp_insitu = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_field, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$salinity_field,Pt=0,Sit=0))

pH_durafet <- d %>%
  dplyr::filter(!is.na(pH_s_durafet))
pH_durafet <- pH_durafet %>%
  dplyr::mutate(pH_s_durafet_temp_insitu = pHinsi(pH=pH_durafet$pH_s_durafet,ALK=pH_durafet$at_mean_interp*1e-6, Tinsi=pH_durafet$temp_field, Tlab=pH_durafet$temp_s_lab, Pinsi= pH_durafet$depth/10, S=pH_durafet$salinity_field,Pt=0,Sit=0))

# create separate seafet/durafet df to join to initial "d" df
pH_seafet_mean <- pH_seafet%>%
  dplyr::select(datetime,pH_s_seafet_temp_insitu)%>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(pH_s_seafet_temp_insitu = mean(pH_s_seafet_temp_insitu, na.rm = T))
pH_durafet_mean <- pH_durafet%>%
  dplyr::select(datetime,pH_s_durafet_temp_insitu)%>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(pH_s_durafet_temp_insitu = mean(pH_s_durafet_temp_insitu, na.rm = T))

@@

```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour.rds"))
# load = d_hour
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT_filtered, NA), # beginning of data series for AT
         AT_filtered = ifelse(AT_filtered == "NaN", NA, AT_filtered), #3 columns are character
         #pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
         #PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
         ) %>%
  dplyr::rename(at_contros=AT,pco2_contros=PCO2_corr_contros_filtered,pH_durafet=HW_pH1_filtered,temp_insitu_11m=temp_insitu_11m_filtered, sal_fb = sal_fb_filtered, sal_insitu_ctd = sal_insitu_ctd_filtered, temp_fb = temp_fb_filtered, temp_insitu_ctd = temp_insitu_ctd_filtered)
```

@@

# seaFET pH 
# closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
# discrete$closest_datetime <- d_all$datetime[closest]
# # if the closest value is more than 30 min away, then we do not take it
# discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, pH_s_seafet_temp_insitu) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")
# #voltINT
# discrete2merge <- discrete %>%
#   #drop_na() %>%
#   dplyr::select(closest_datetime, voltINT) %>%
#   rename(datetime=closest_datetime)
# d_all <- full_join(d_all, discrete2merge, by="datetime")
# #voltEXT
# discrete2merge <- discrete %>%
#   #drop_na() %>%
#   dplyr::select(closest_datetime, voltEXT) %>%
#   rename(datetime=closest_datetime)
# d_all <- full_join(d_all, discrete2merge, by="datetime")

# duraFET pH 
# closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
# discrete$closest_datetime <- d_all$datetime[closest]
# # if the closest value is more than 30 min away, then we do not take it
# discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, pH_s_durafet_temp_insitu) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

@@

```{r Sal filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
#### filter salinities above 28
d_all <- d_all%>%
  dplyr::mutate( sal_fb = ifelse(sal_fb <28, NA, sal_fb),
                 sal_insitu_ctd = ifelse(sal_insitu_ctd <28, NA, sal_insitu_ctd))
 d_all <- d_all%>%
  dplyr::mutate(sal_insitu_ctd = ifelse(datetime > "2019-12-26 00:00:00", NA, sal_insitu_ctd))

########### Binding sal_fb + sal_insitu if we get gaps in sal_insitu = call this new column = sal_mix ########### 
d_all <- d_all %>%
  dplyr::mutate(sal_mix = ifelse(!is.na(sal_fb), sal_fb, 
                               ifelse (pressure_insitu_ctd_filtered >=8 ,sal_insitu_ctd, NA )))
### remove sal_mix datat that seem to be to high compared to sal_fb
  d_all <- d_all%>%
  dplyr::mutate(sal_mix = ifelse(datetime > "2018-03-09 00:00:00" & datetime < "2018-04-13 18:00:00" , NA, 
                          ifelse(datetime > "2018-05-21 19:00:00" & datetime < "2018-05-24 17:00:00" , NA,
                          ifelse(datetime > "2018-05-28 06:00:00" & datetime < "2018-06-03 13:00:00" , NA,
                          ifelse(datetime > "2018-06-16 06:00:00" & datetime < "2018-06-21 05:00:00" , NA,
                          ifelse(datetime > "2019-12-02 08:00:00" & datetime < "2019-12-03 08:00:00" , NA,
                          ifelse(datetime > "2019-12-09 07:00:00" & datetime < "2019-12-09 10:00:00" , NA, 
                          ifelse(datetime > "2019-12-09 15:00:00" & datetime < "2019-12-09 18:00:00" , NA,
                          ifelse(datetime > "2019-12-10 14:00:00" & datetime < "2019-12-10 18:00:00", NA, sal_mix)))))))))

```{r Temp filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
###### Binding temp_insitu_11m + temp_insitu_ctd if we get gaps in temp_insitu_11m = call this new column = temp_mix ####### 
d_all <- d_all %>%
  dplyr::mutate(temp_mix = ifelse(!is.na(temp_insitu_11m), temp_insitu_11m, 
                               ifelse (pressure_insitu_ctd_filtered >=8 ,temp_insitu_ctd, NA )))
```

@@

#SAL MIX
sal_xts <- dplyr::select(d_all, datetime, sal_mix)

@@

      dySeries("sal_mix", color = "blue", strokeWidth = 0, label = "S") %>%

@@

temp_insitu_xts <- dplyr::select(d_all, datetime, temp_mix)

@@

dygraph(temp_insitu_xts, group = "awipev", main="Temperature (in situ 11 m)", ylab="Temperature") %>%
      dySeries("temp_mix", color = "blue", strokeWidth = 0, label = "T") %>%

@@

durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_insitu)

@@

    dySeries("pH_s_durafet_temp_insitu", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%

@@

seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_insitu)

@@

  dySeries("pH_s_seafet_temp_insitu", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%

@@

## Salinities
Several salinity sensors are on site, 1 inside the Ferrybox (SBE45) and 5 outside (ctd183, ctd181, ctd578, ctd964/964b and ctd103) that are switched periodically. Salinity from FB is taken in consideration. If data gaps are encountered, they are filled with bottom salinty data from ctd (> 8 m). New column "sal_mix" is created.

- 1 SBE45 inside the Ferrybox (sal_fb)
- 5 CTD > 8 meters depth (sal_insitu_ctd)

### **Sal FB / Sal CTD > 8 m **

Property-property salinity plot using:

fit <- lmodel2(data = d_all%>%dplyr::filter(pressure_insitu_ctd_filtered >=8),  sal_fb ~ sal_insitu_ctd , nperm = 99)

```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
fit <- lmodel2(data = d_all%>%dplyr::filter(pressure_insitu_ctd_filtered >=8),  sal_fb ~ sal_insitu_ctd , nperm = 99)

p_sal_fb_sal_insitu<-  ggplot(d_all,aes(x=sal_insitu_ctd, y= sal_fb, label = month))+
  geom_text( aes(color=factor(month))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_line(aes(x = sal_fb, y = sal_fb), linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("Sal in situ vs Sal FB","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
  labs( x="Salinity insitu", y="Salinity FB ", color = "Months")  +theme_bw()
print(p_sal_fb_sal_insitu)

# # PLOT
# seafet_contros_xts <- dplyr::select(d_all, datetime, temp_insitu_11m, temp_insitu_ctd, pressure_insitu_ctd_filtered, temp_mix, sal_mix)
# seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
# dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
# dySeries("temp_insitu_11m", label = "temp_insitu_11m", color ="red",axis= "y2", strokeWidth=0, pointSize=4) %>%
# dySeries("temp_insitu_ctd", label = "temp_insitu_ctd", color ="blue",axis= "y2", strokeWidth=0, pointSize=3) %>%
# dySeries("temp_mix", label = "temp_mix", color ="green",axis= "y2", strokeWidth=0, pointSize=2) %>%
# dySeries("sal_mix", label = "sal_mix", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%
# dySeries("pressure_insitu_ctd_filtered", label = "pressure_insitu_ctd_filtered", color ="black", strokeWidth=0, pointSize=2) %>%
#   dyLegend(show = "onmouseover")   %>%
#   #dyAxis( "y2",valueRange = c(-3, 36))%>%
#   dyAxis( "y2",valueRange = c(-3, 36))%>%
#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
#   dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
#   dyRangeSelector(height = 30, dateWindow= NULL)

# #Plot for philipp
# sal_15 <- ggplot(data= d_all%>%dplyr::filter(datetime > "2015-10-01 00:00:00" & datetime < "2015-12-31 00:00:00"), aes(x=datetime,  colour = "salinity"))+ 
# geom_point(aes(y=sal_fb,col="FB") , size=2) +
# geom_point(aes(y=sal_insitu, col="in situ"))  +
# labs(title=  "salinity 2015", x = "Time", y= "")
# 
# sal_19 <-ggplot(data= d_all%>%dplyr::filter(datetime > "2019-10-01 00:00:00" & datetime < "2019-12-31 00:00:00"), aes(x=datetime,  colour = "salinity"))+ 
# geom_point(aes(y=sal_fb,col="FB") , size=2) +
# geom_point(aes(y=sal_insitu, col="in situ"))  +
# labs(title=  "salinity 2019", x = "Time", y= "")
# 
# ggsave("figures/sal_2019.png", sal_19, units="cm")
# ggsave("figures/sal_2015.png", sal_15, units="cm")
# ggsave("figures/sal_property.png", p_sal_fb_sal_insitu, units="cm")

@@

The mean difference between salinity FB and in situ is: `r mean_diff_sal_fb_insitu` ± `r sd_diff_sal_fb_insitu` PSU.

## Temperatures
Several temperature sensors are on site, 1 inside the Ferrybox (SBE45), 5 outside (ctd183, ctd181, ctd578, ctd964/964b and ctd103) that are switched periodically and 1 fixed at 11 m depth (sbe38). 
Temperature in situ at 11 m depth is taken in consideration. If data gaps are encountered, they are filled with bottom temperature data from ctd (> 8 m). New column "temp_mix" is created. For the moment, no gaps are encountered and temp_mix = temp_insitu_11m.

- 1 SBE45 inside the Ferrybox (temp_fb)
- 5 CTD > 8 meters depth (sal_insitu_ctd)
- 5 fixed at 11 meters depth (sal_insitu_11m)

@@

### **T seaFET / T mix **

Property-property temperature plot using:

fit <- lmodel2(data = d_all,  T_seaF ~ temp_mix , nperm = 99)

```{r Temp comparaison, echo=FALSE, message= FALSE, warning=FALSE}
# seaF outliers (T - volt int - volt ext) to remove from 2017-12-10 to 2017-12-14
d_all <- d_all %>%
  dplyr::mutate(T_seaF = ifelse(datetime >= "2017-12-10 11:00:00" & datetime <= "2017-12-14 12:00:00", NA, T_seaF),
                voltINT = ifelse(datetime >= "2017-12-10 11:00:00" & datetime <= "2017-12-14 12:00:00", NA, voltINT), 
                voltEXT = ifelse(datetime >= "2017-12-10 11:00:00" & datetime <= "2017-12-14 12:00:00", NA, voltEXT))

fit <- lmodel2(data = d_all,  T_seaF ~ temp_mix , nperm = 99)

pTseaf_Tinsi<-  ggplot(d_all,aes(x=temp_mix, y= T_seaF, label = month))+
  geom_text( aes(color=factor(month))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_line(aes(x = T_seaF, y = T_seaF), linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("T seaF vs T insi","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
  labs( x="T insi", y="T seaF ", color = "Months")  +theme_bw()
print(pTseaf_Tinsi)

d_all$diff_T_seaF_insitu <- d_all$T_seaF - d_all$temp_mix
mean_diff_T_seaF_insitu <- round(mean(d_all$diff_T_seaF_insitu, na.rm = TRUE), digits = 2)
sd_diff_T_seaF_insitu <- round(sd(d_all$diff_T_seaF_insitu, na.rm = TRUE), digits = 2)

@@

### **T Ferrybox / T mix **

Property-property temperature plot using:

fit <- lmodel2(data = d_all,  temp_fb ~ temp_mix , nperm = 99)

```{r Temp fb insi comparaison, echo=FALSE, message= FALSE, warning=FALSE}
# Remove temp_fb outliers 
d_all <- d_all %>%
  dplyr::mutate(temp_fb = ifelse(datetime >= "2017-03-22 08:00:00" & datetime <= "2017-03-23 16:00:00", NA, temp_fb),
                temp_fb = ifelse(temp_fb >15, NA, temp_fb))

fit <- lmodel2(data = d_all,  temp_fb ~ temp_mix , nperm = 99)

pTfb_Tinsi<-  ggplot(d_all,aes(x=temp_mix, y= temp_fb, label = month))+
  geom_text( aes(color=factor(month))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_line(aes(x = temp_fb, y = temp_fb), linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("T FB vs T insi","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
  labs( x="T insi", y="T FB ", color = "Months")  +theme_bw()
print(pTfb_Tinsi)

d_all$diff_T_fb_insitu <- d_all$T_seaF - d_all$temp_mix
mean_diff_T_fb_insitu <- round(mean(d_all$diff_T_fb_insitu, na.rm = TRUE), digits = 2)
sd_diff_T_fb_insitu <- round(sd(d_all$diff_T_fb_insitu, na.rm = TRUE), digits = 2)
```

@@

### **T 11 m / T CTD > 8 m **

Property-property temperature plot using:

fit <- lmodel2(data = d_all%>%dplyr::filter(pressure_insitu_ctd_filtered >=8),  temp_insitu_11m ~ temp_insitu_ctd , nperm = 99)

```{r Temp fb insi comparaison, echo=FALSE, message= FALSE, warning=FALSE}

fit <- lmodel2(data = d_all%>%dplyr::filter(pressure_insitu_ctd_filtered >=8),  temp_insitu_11m ~ temp_insitu_ctd , nperm = 99)

p<-  ggplot(d_all,aes(x=temp_insitu_ctd, y= temp_insitu_11m, label = month))+
  geom_text( aes(color=factor(month))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_line(aes(x = temp_insitu_11m, y = temp_insitu_11m), linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("T FB vs T insi","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
  labs( x="T insi", y="T FB ", color = "Months")  +theme_bw()
print(p)

d_all$diff_T_fb_insitu <- d_all$T_seaF - d_all$temp_insitu_ctd
mean_diff_T_fb_insitu <- round(mean(d_all$diff_T_fb_insitu, na.rm = TRUE), digits = 2)
sd_diff_T_fb_insitu <- round(sd(d_all$diff_T_fb_insitu, na.rm = TRUE), digits = 2)
```

@@

@@

```{r Discrete salinity vs TA, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%", fig.align="center"}
d_all_at_discrete <- d_all %>% #  To remove an outlier in red
  dplyr::select(datetime, month,closest_datetime, at, sal_mix) #%>%
 # dplyr::filter( !is.na(at) & !is.na(sal) & sal >30)

@@

#fit <- lm(data = drop_na(d_all_at_discrete, at), at ~ sal)
fit <- lm(data = d_all_at_discrete, at ~ sal_mix)
slope_s_at <- fit$coefficients[[2]]
intercept_s_at <- fit$coefficients[[1]]
# at_s <- ggreg(fit)+ labs(x="Salinity", y="Discrete TA") + Mytheme()

at_s <- ggplot(d_all_at_discrete,aes(x=sal_mix, y= at, label = month))+
  geom_text( aes(color=factor(month))) +
  scale_color_discrete(guide="none")+
    labs(x="Salinity", y="Discrete AT", color = "Months")  +
    stat_smooth(method = "lm", col = "black") +
    labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
                       ";\nSlope =",signif(fit$coef[[2]], 5),
                       ";\nP =",signif(summary(fit)$coef[2,4], 5))) +
  theme_bw() +
  theme(aspect.ratio=1,
        axis.text=element_text(size=15),
        axis.title.y= element_text(size =15),
        axis.title.x= element_text(size =15),
        plot.margin = unit(c(0.5,1,1,1), "cm"),
        plot.title = element_text(size=15, hjust=0.05,margin = margin(l = 10, b = -70)))
  #print(at_s)
